BLAST: Block Applications for Things

### 2022-04-08 demo-eswc22/paper/paper.tex
add exception to used Blockly guidelines

The editor uses the Blockly library and provides custom control and command blocks that make up the BLAST language. The custom blocks and the BLAST environment follow all the important design principles introduced by Fraser \cite{fraser}, such as a clear border style or the avoidance of transitive connections.
Based on the user's arrangement of these blocks, the editor generates JavaScript code that can then be executed in the browser.
The system builds on the Web Bluetooth API\footnote{\url{https://webbluetoothcg.github.io/web-bluetooth/}} and the WebHID API\footnote{\url{https://wicg.github.io/webhid/}} to interact with devices.
BLAST uses the Web of Things abstraction as interface; we have implemented the WoT interface for eight devices that use the BLE GAP and GATT profiles as well as the USB and Bluetooth HID interface.
The WoT interface contains the metadata and interaction affordances as well as the JavaScript code needed for communication.
In addition, the system includes access to the camera and sound output via browser APIs using the WoT interface.
Further, the system includes access to the Web Speech API\footnote{\url{https://wicg.github.io/speech-api/}}.
The functionality to issue HTTP requests is based on the Fetch API\footnote{\url{https://fetch.spec.whatwg.org/}}, Social Linked Data (Solid) authentication is based on the Inrupt client libraries\footnote{\url{https://docs.inrupt.com/developer-tools/javascript/client-libraries/}}, and SPARQL query support is based on µRDF.js\footnote{\url{https://github.com/vcharpenay/uRDF.js/}}.
Next to the presented small scenario around geofences, we have also developed BLAST programs to accomplish five use cases\footnote{TODO: URI to videos} with varying complexity. Each use case introduces a different challenge that requires the use of programming patterns in combination with the built-in blocks for properties, actions, events, requests, and queries.

>>>>

The editor uses the Blockly library and provides custom control and command blocks that make up the BLAST language. The custom blocks and the BLAST environment follow almost all of the design principles introduced by Fraser \cite{fraser}, such as a clear border style or the avoidance of transitive connections. Not implemented, however, are the varying color choices for different loops.

Based on the user's arrangement of the blocks, the editor generates JavaScript code that can then be executed in the browser.
The system builds on the Web Bluetooth API\footnote{\url{https://webbluetoothcg.github.io/web-bluetooth/}} and the WebHID API\footnote{\url{https://wicg.github.io/webhid/}} to interact with devices.
BLAST uses the Web of Things abstraction as interface; we have implemented the WoT interface for eight devices that use the BLE GAP and GATT profiles as well as the USB and Bluetooth HID interface.
The WoT interface contains the metadata and interaction affordances as well as the JavaScript code needed for communication.
In addition, the system includes access to the camera and sound output via browser APIs using the WoT interface.
Further, the system includes access to the Web Speech API\footnote{\url{https://wicg.github.io/speech-api/}}.
The functionality to issue HTTP requests is based on the Fetch API\footnote{\url{https://fetch.spec.whatwg.org/}}, Social Linked Data (Solid) authentication is based on the Inrupt client libraries\footnote{\url{https://docs.inrupt.com/developer-tools/javascript/client-libraries/}}, and SPARQL query support is based on µRDF.js\footnote{\url{https://github.com/vcharpenay/uRDF.js/}}.
Next to the presented small scenario around geofences, we have also developed BLAST programs to accomplish five use cases\footnote{TODO: URI to videos} with varying complexity. Each use case introduces a different challenge that requires the use of programming patterns in combination with the built-in blocks for properties, actions, events, requests, and queries.
